Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-16 main.Rmd
cricket data example 2 write up updated

Another question that can be addressed is if good fielding (defending) affects the scoring rate in the subsequent over? To measure the fielding quality, we use an indicator function on dismissals (1 if there was at least one wicket in the previous over due to a run out or catch, 0 otherwise). The scoring rate is measured by runs per over. \autoref{fig:cricex}b shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over compared to the case when there has been at least one dismissal in the previous over. Thus, dismissals lead a batsman to adopt a more defensive play style. This seems to be unaffected by the over of the innings (the facet variable).

>>>>

Another question that can be addressed is if good fielding or bowling (defending) in the previous over affects the scoring rate in the subsequent over? To measure the fielding and bowling quality, we use an indicator function on dismissals (1 if there was at least one wicket in the previous over, 0 otherwise). The scoring rate is measured by runs per over. \autoref{fig:cricex}b shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over compared to the case when there has been at least one dismissal in the previous over. This seems to be unaffected by the over of the innings (the facet variable). This might be because the new batsman needs to play himself in or the dismissals lead the (not-dismissed) batsman to adopt a more defensive play style. Run rates will also vary depending on which player is facing the next over and when the wicket falls in the previous over.
